Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-08 paper.tex
wording

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes\footnote{Python does not actually
distinguish between public and private  attributes or methods. By convention
however, any identifier prefixed with an underscore is considered a non-public
part of the API~\citep{pythontut}.} and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, appropriate default hyper-parameter values are provided for all
built-in estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible \textit{out-of-box}
for non-experts. Finally, the constructor of an estimator never performs
any actual learning, nor does it even see any training dataset. Its only goal is
to set the parameter values and freeze the behavior of the estimator.

The estimator interface also defines a \texttt{fit} method. Invoking this method
causes the estimator to learn from a training set (e.g., supplied as two arrays
\texttt{X} and \texttt{y} in supervised learning estimators). Its task, from an
API point of view, is to run a learning algorithm and to determine model-
specific  parameters from the training data and set these as attributes on the
estimator object. As a convention, the parameters learned by an estimator are
exposed as public attributes\footnote{Note that the learned parameters are
different from the hyper-parameters given to the constructor. To distinguish
between the two, learned parameters are all suffixed with a trailing underscore
(e.g., \texttt{clf.coef\_} in the case of linear models is the vector of
coefficients learned from the data).} on the trained object.

>>>>

The constructor of an estimator object takes as input a set of named constant
hyper-parameters. At initialization, all given parameters are attached to the
estimator instance as public attributes\footnote{Python does not actually
distinguish between public and private  attributes or methods. By convention
however, any identifier prefixed with an underscore is considered a non-public
part of the API~\citep{pythontut}.} and serve to determine the estimator
behavior (e.g., the $C$ constant in SVMs). Parameters set as public attributes
are also used for introspection purposes, e.g., in model selection routines. To
ease their use, default hyper-parameter values are provided for all
built-in estimators. These default values are set to be relevant in most common
situations in order to make estimators as efficient as possible \textit{out-of-box}
for non-experts. Finally, the constructor of an estimator never performs
any actual learning, nor does it even see any training dataset. Its only goal is
to set the parameter values and freeze the behavior of the estimator.

The estimator interface defines a \texttt{fit} method. This method is
called with training data (e.g., supplied as two arrays
\texttt{X} and \texttt{y} in supervised learning estimators). Its task
is to run a learning algorithm and to determine model-
specific parameters from the training data and set these as attributes on the
estimator object. As a convention, the parameters learned by an estimator are
exposed as public attributes\footnote{Note that the learned parameters are
different from the hyper-parameters given to the constructor. To distinguish
between the two, learned parameters are all suffixed with a trailing underscore
(e.g., \texttt{clf.coef\_} in the case of linear models is the vector of
coefficients learned from the data).} on the trained object.
